### 2002-08-22 dialoguesisters/de/CC67.tex
no message

\noindent\emph{Anmerkung zu CrypTool:}
\\
Mit CrypTool, Version 1.3 und h"oher kann man diese Variante der
RSA-Verschl"usselung folgenderma"sen nachvollziehen:
\\
Men"u \textbf{Einzelverfahren / RSA-Demo / RSA-Kryptosystem\dots}.
\\
Im Dialog \textbf{Das RSA-Kryptosystem} dann die zweite Option w"ahlen --
nur die "offentlichen Parameter sind bekannt -- und dann faktorisieren. Die
zwei gegebenen Code-Zahlen (z.~B. 51,3) von Bianca und Doris hei"sen hier
$N$ und $e$. Der Algorithmus kann "uber den Knopf \textbf{Optionen f"ur
  Alphabet und Zahlensystem\dots} f"ur diese spezielle Variante
parametrisiert werden: im folgenden Dialog \textbf{Optionen f"ur die
  RSA-Verschl"usselung} dann \textbf{Dialog der Schwestern} ausw"ahlen und
das Alphabet auf genau die 26 Buchstaben (A, B, \dots, Y, Z) beschr"anken.

>>>>

\noindent\emph{Anmerkung zu CrypTool:}
\\
Mit CrypTool, Version 1.3 und h"oher kann man diese Variante der
RSA-Verschl"usselung folgenderma"sen nachvollziehen:
\\
Men"u \textbf{Einzelverfahren / RSA-Demo / RSA-Kryptosystem\dots}.
\\
Im folgenden Dialog \textbf{Das RSA-Kryptosystem} dann die zweite Option w"ahlen --
nur die "offentlichen Parameter sind bekannt -- und dann faktorisieren. Die
zwei gegebenen Code-Zahlen (Beispiel: 51,3) von Bianca und Doris hei"sen hier
$N$ und $e$. Der Algorithmus kann "uber den Knopf \textbf{Optionen f"ur
Alphabet und Zahlensystem\dots} f"ur diese spezielle Variante
parametrisiert werden: \\
Im folgenden Dialog \textbf{Optionen f"ur die
RSA-Verschl"usselung} dann \textbf{Dialog der Schwestern} ausw"ahlen und
das Alphabet auf genau die 26 Buchstaben (A, B, \dots, Y, Z) beschr"anken.

### 2002-08-22 dialoguesisters/en/DialogueSisters.tex
no message

\item[(4)] One finds details to this RSA-procedure in the following book: {\small
  NEAL KOBLITZ}, {\em A Course in Number Theory and Cryptography\/},
second edition, chapter IV, paragraph 2; Springer-Verlag, 1994. \\
\end{itemize}
\[\]
\hrulefill
\[\]
\[\]
{\em Note of the translator:} \\
I want to thank Mr Richard Christensen for his review of this translation.
\\[1ex]
With CrypTool version 1.3 and higher it is easy to comprehend this variant of the RSA encryption scheme by using 
the following steps: \\
menu {\bf Indiv. Procedures / RSA Demonstration / RSA Cryptosystem}. Within this dialog box 
{\bf The RSA Cryptosystem} choose the second option -- knowing only public parameters -- and factorize N. The given 
two code numbers (e.g. 51, 3) of Bianca and Doris are N and e. The algorithms behind can be switched to this 
special variant by hitting the button \textbf{Options for alphabet and number system...}. In the following dialog 
box {\bf Options for RSA Encryption} select \textbf{Dialogue of the Sisters} and limit the alphabet to exactly 26 
letters (A, B, ..., Y, Z).

>>>>

\item[(4)] One finds details to this RSA-procedure in the following book: {\small
  NEAL KOBLITZ}, {\em A Course in Number Theory and Cryptography\/},
second edition, chapter IV, paragraph 2; Springer-Verlag, 1994. \\
\end{itemize}
\[\]
\hrulefill
\[\]
\[\]
{\em Note of the translator:} \\
I want to thank Mr Richard Christensen for his review of this translation.
\\[1ex]
With CrypTool version 1.3 and higher it is easy to comprehend this variant of the RSA encryption scheme by using 
the following steps: \\
menu {\bf Indiv. Procedures / RSA Demonstration / RSA Cryptosystem\dots}. \\
Within the following dialog box {\bf The RSA Cryptosystem} choose the second option -- knowing only public parameters -- and factorize N. The given 
two code numbers (e.g. 51, 3) of Bianca and Doris are N and e. The algorithms behind can be switched to this 
special variant by hitting the button \textbf{Options for alphabet and number system\dots}. \\
In the following dialog 
box {\bf Options for RSA Encryption} select \textbf{Dialogue of the Sisters} and limit the alphabet to exactly 26 
letters (A, B, ..., Y, Z).
